### 2022-12-02 writing/manuscript.Rmd
removing old bootstrap code from Rmd and adding comments

```{r eval=FALSE, include=FALSE}

# This chunk defines the function used to bootstrap random pairs of countries, correlated their responses on a given scale, and store the coefficient (in `cors`). 
# To save time while knitting this document, this chunk will not be executed. Instead, results of the bootstrapping procedure are read in from results/bootstrap_res2.csv.

set.seed(1)

webraw <- filter(fulldata, study == "web")

# randomly select two industrialised cohorts, compute their song-wise mean ratings, and store their correlation.

boot2 <- function(type, n = 500000) {
  cors <- c()

  for (i in 1:n) {
    cohorts <- sample(unique(webraw$cohort),2)

    c1 <- fulldata[fulldata$cohort==cohorts[1],]
    c2 <- fulldata[fulldata$cohort==cohorts[2],]

    c1 <- c1 %>% 
      group_by(song, songfunction) %>% 
      summarize(mean_danc = mean(danc, na.rm = T),
                mean_heal = mean(heal, na.rm = T),
                mean_baby = mean(baby, na.rm = T),
                mean_love = mean(love, na.rm = T)) 
    c2 <- c2 %>% 
      group_by(song, songfunction) %>% 
      summarize(mean_danc = mean(danc, na.rm = T),
                mean_heal = mean(heal, na.rm = T),
                mean_baby = mean(baby, na.rm = T),
                mean_love = mean(love, na.rm = T))

    if (type == "danc") {
      cors[i] <- cor.test(c1$mean_danc, c2$mean_danc)$estimate
    } else if (type =="baby") {
      cors[i] <- cor.test(c1$mean_baby, c2$mean_baby)$estimate
    } else if (type =="heal") {
      cors[i] <- cor.test(c1$mean_heal, c2$mean_heal)$estimate
    }else if (type =="love") {
      cors[i] <- cor.test(c1$mean_love, c2$mean_love)$estimate
    } else {
      warning("Incorrect input.")
    }
  }

  return(cors)
}

danccors <- suppressMessages(boot2("danc"))
babycors <- suppressMessages(boot2("baby"))
healcors <- suppressMessages(boot2("heal"))
lovecors <- suppressMessages(boot2("love"))

within_cors <- cbind(danccors, babycors, healcors, lovecors)
write.csv(within_cors,here("results", "bootstrap_res2.csv"), row.names = FALSE)

@@

# test hypothesis that tru correlation > 0 for each song type
boots <- read_csv(here("results","bootstrap_res2.csv")) %>% 
  map(~ t.test(.x, mu = 0, alternative = "greater") %>% tidy)

@@

```{r include=FALSE}
# This chunk of code uses a previously generated bootstrapped dataset found in results/bootstrap_res.csv.
boot <- read.csv(here("results", "bootstrap_res.csv"))

>>>>

@@

# test hypothesis that tru correlation > 0 for each song type,
# see analysis/bootstrap_analyses.R for details
boots <- read_csv(here("results","bootstrap_res2.csv")) %>% 
  map(~ t.test(.x, mu = 0, alternative = "greater") %>% tidy)

@@

```{r include=FALSE}
# This chunk of code uses a previously generated bootstrapped dataset found in results/bootstrap_res.csv.
# see analysis/bootstrap_analyses.R for details
boot <- read.csv(here("results", "bootstrap_res.csv"))
